Supplement

### 2023-06-02 paper/supplement.qmd
Plot cdiff OTU 25 relabun & feature importance
no significant differences between severe and not severe.
feature importance not signifcantly different from zero.

---
title: 'Supplement'
fontsize: 11pt
mainfont: Helvetica
format:
  pdf:
    keep-tex: false
    linenumbers: true
    doublespacing: true
    lof: false
crossref:
  fig-title: FIG S
---

::: {#fig-performance fig-cap="**Precision-recall curves.**"}
![](figures/prc_curves.png)
:::

>>>>

---
title: 'Supplement'
fontsize: 11pt
format:
  pdf:
    keep-tex: false
    linenumbers: true
    doublespacing: true
    lof: false
crossref:
  fig-title: FIG S
---

::: {#fig-prc fig-cap="**Precision-recall curves.**
The original precision-recall curves for each model.
The horizontal line is the baseline precision, i.e. the proportion of severe
cases in the dataset for each severity definition.
Since each definition has a different baseline precision, the PRCs cannot be
compared directly without balancing the precision (see Figure 2).
"}
![](figures/prc_curves.png)
:::

::: {#fig-cdiff fig-cap="**_C. difficile_ relative abundance and feature importance.**
Of the 45 OTUs belonging to the _Peptostreptococcaceae_ family, only one
(OTU 25) had abundance values above the limit of detection.
**Left**: log~10~-transformed relative abundance of OTU 25 in the full datasets.
The dashed line is the limit of detection.
**Right**: Permutation feature importance as measured by AUROC for OTU 25.
The dotted line is a feature importance of zero, meaning the feature is not
significant.
"}
![](figures/cdiff-otu.png)
:::
